Improving practices in a medium french company: First step

### 2019-11-26 __latexindent_temp.tex
Nicolas correction

\section{Related Work}
%-------------------------------------------------------------------------------
\label{sec:related-work}
Recently, research on mining software repositories has received much attention as it has attempted to  understand  software  evolution \cite{Zhan10a}. Software defect history and source code history are often used to monitor software maintenance or predict the number of defect in a system. 
For instance, software defect prediction using software repositories, has already been extensively discussed in literature in numerous publications.
This literature is summarised in many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
%"intro": de quoi on va parler et pourquoi en parler ?

@@

%Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
 \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
Dan Port and Bill Taber \cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution for maintenance monitoring.

In this paper, we are interested to evaluate the system to monitor the re-engineering of the system. But we do not have the source code historical data. Thus, we cannot use the methods presented in above-mentionned literature. We develop a lightweight technique to analyse the ticket database .
%"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
%donc: on develop notre propre analyse sur la ticket db.

\section{Defect Model}
%-------------------------------------------------------------------------------
\label{sec:defectModel}

@@

\subsection{Presentation of the studied system}
%-------------------------------------------------------------------------------
Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
This is the case of the studied system  which has more than 20 years. 
It's a 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
The system is not versioned and old versions are lost until 2012.

Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
Powerbuilder applications components are grouped by libraries.  
A Powerbuilder library contains differents type of Objects: Datawindow, User object, Global function,  menu, etc. 
Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
Its version 2017 supports version control systems.% and the support is not stable.

A ticket is related do a task to do. 
This task can be fixing a defect, writing documentation, adding a new feature, etc. 
A ticket is open for a task . 
Once the task is done and validated, the ticket is close.
A ticket has the following characteristics:

\begin{itemize}
\item the libraries it  is related to
\item the creation date
\item the closing date
\item time spent by a developer
  \begin{itemize}
\item time to analyze
\item time to implement solution
\item time to test
  \end{itemize}
\item  the estimation of the time needed by the developer to work on the ticket
\end{itemize}
In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.

>>>>

\section{Related Work}
%-------------------------------------------------------------------------------
\label{sec:related-work}
Recently, research on mining software repositories has received much attention as it attempts to  understand  software  evolution \cite{Zhan10a}.
Software defect history and source code history are often used to monitor software maintenance or predict the system's quality. 
For instance, software defect prediction using software repositories, has already been extensively discussed in literature as witnessed by many literature surveys: \cite{Catal09,Hall12,Hoss17,Li19a,malh15}.
%"intro": de quoi on va parler et pourquoi en parler ?

@@

%Software defect history can be used alone to build a software defect model using statistical techniques or machine learning algorithms to predict post-release defects in software.
But these solutions rely on the availability of source code history. 
For example, \cite{gill91} used McCabe’s cyclomatic complexity metric divided by the size of the system to predict software maintenance productivity.
\cite{port18,Zhan10a} used software defect history and source code history to assess a system evolution to monitor maintenance.

In our case, the source code history is not easily available as the company does not make use of a version control system.
Thus, we cannot use the methods presented above.

Other researchers considered ticket database to characterize a system.

We develop a lightweight technique to analyse the ticket database.

%"conclusion": (1) on ne veut pas faire de prediction (2) on n'a pas d'historique de code
%donc: on develop notre propre analyse sur la ticket db.

\section{Study background}
%-------------------------------------------------------------------------------
\label{sec:defectModel}

In this paper, we are interested in characterising the system and its evolution to better evaluate the possible future impact of our intervention.

\subsection{Presentation of the studied system}
%-------------------------------------------------------------------------------

Legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
This is the case of the system we are studying which is older than 20 years. 
It's a 3 MLOC software written in Powerbuilder.

Powerbuilder is a programming language and integrated development environment initially developed by PowerSoft. The first version was published in 1992.
Powerbuilder application components are grouped in libraries.  
A Powerbuilder library contains differents type of objects: datawindow, user object, global function,  menu, etc. 
Powerbuilder is not totally object-oriented, as inheritance and object-oriented features are limited to some object types (Windows, Userobjects and Menus). 
Its 2017 version  supports version control but for historical reasons it was never used on the system studied.% and the support is not stable.

With 117 Powerbuilder libraries, the  bigest library is  over 300 KLOC.
The system is not versioned in a version control system but some old major versions or archivied in separate directories.
Old versions (before 2012) are completely lost.

A ticket is related do a task to do and it is used for billing. 
This task can be fixing a defect, writing documentation, adding a new feature, etc. 
Once the task is done and validated, the ticket is close.
At CIM, a ticket has the following characteristics:

\begin{itemize}
\item the creation date
\item the closing date
\item the library(ies) it is related to
\item time spent by a developer
  \begin{itemize}
\item time to analyze
\item time to implement solution
\item time to test
  \end{itemize}
\item  the estimation of the time needed by the developer to work on the ticket
\end{itemize}
In this paper we use defect history  from tickets database to build a simple defect model that evaluate developers effort.

@@
